Variational Monte Carlo on bosonic systems

### 2018-03-20 project_1/article/article.tex
Finally added the appendix figure for problem b
Add plots and tables for problem b

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include package for drawing Feynman diagrams
\usepackage{tikz-feynman}
% Include package for typesetting contractions
\usepackage{simpler-wick}
% Include the Feynman-slash
\usepackage{slashed}
% Include Tikz
\usepackage{tikz}
% Several figures in the same figure
\usepackage{subfig}

@@

	\begin{table}
		\caption{Analytic result. $N=1$, 1D, $2\times10^6$ cycles.}
		\centering
		\begin{tabular}{ccc} \hline
			\alpha & E($\alpha$) & $\sigma^2$(E) \\ \hline \hline
				0.30 & 0.5717 & 0.1504 \\
				0.34 & 0.5397 & 0.0815 \\
				0.38 & 0.5197 & 0.0390 \\
				0.42 & 0.5084 & 0.0154 \\
				0.46 & 0.5016 & 0.0034 \\
				0.50 & 0.5000 & 0.0000 \\
				0.54 & 0.5016 & 0.0030 \\
				0.58 & 0.5047 & 0.0117 \\
				0.62 & 0.5114 & 0.0239 \\
				0.66 & 0.5203 & 0.0381 \\
				0.70 & 0.5275 & 0.0590 \\ \hline \hline			
		\end{tabular}	
	\end{table}

	\begin{table}
		\caption{Numerical result. $N=1$, 1D, $2\times10^6$ cycles.}
		\centering
		\begin{tabular}{ccc} \hline
			\alpha & E($\alpha$) & $\sigma^2$(E) \\ \hline \hline
				0.30 & 0.5807 & 0.2535 \\
				0.34 & 0.5379 & 0.1280 \\
				0.38 & 0.5365 & 0.1120 \\
				0.42 & 0.5220 & 0.0671 \\
				0.46 & 0.5210 & 0.05250 \\
				0.50 & 0.5265 & 0.0411\\
				0.54 & 0.5264 & 0.0263 \\
				0.58 & 0.5353 & 0.0259 \\
				0.62 & 0.5481 & 0.0221 \\
				0.66 & 0.5481 & 0.0194 \\
				0.70 & 0.5596 & 0.0204 \\ \hline \hline
		\end{tabular}
	\end{table}

@@

\bibliography{references}
\end{document}

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}

@@

    \begin{table}
        \centering
        \caption{One particle in one dimension for the analytic expression with
        $2^{21}$ Monte Carlo cycles and step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$ & $A$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56661&0.00026&0.00133&0.89121&0.39765\\
                0.34&0.53858&0.00019&0.00096&0.88419&0.34550\\
                0.38&0.51822&0.00013&0.00062&0.87823&0.34849\\
                0.42&0.50770&0.00009&0.00037&0.87136&0.36115\\
                0.46&0.50197&0.00004&0.00018&0.86589&0.34705\\
                0.50&0.50000&0.00000&0.00000&0.86092&0.35124\\
                0.54&0.50146&0.00004&0.00016&0.85497&0.34875\\
                0.58&0.50592&0.00007&0.00029&0.84999&0.34705\\
                0.62&0.51180&0.00011&0.00041&0.84455&0.34861\\
                0.66&0.51983&0.00014&0.00051&0.84014&0.36164\\
                0.70&0.52742&0.00017&0.00063&0.83516&0.35525\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_analytic}
    \end{table}

    \begin{table}
        \centering
        \caption{One particle in one dimension for the numeric expression with
        $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56494&0.00026&0.00131&0.89160&0.35031\\
                0.34&0.53933&0.00020&0.00097&0.88427&0.37179\\
                0.38&0.51841&0.00014&0.00063&0.87840&0.34806\\
                0.42&0.50737&0.00008&0.00037&0.87182&0.34957\\
                0.46&0.50211&0.00004&0.00018&0.86549&0.34976\\
                0.50&0.50000&0.00000&0.00000&0.86041&0.34791\\
                0.54&0.50136&0.00004&0.00015&0.85532&0.34858\\
                0.58&0.50525&0.00007&0.00028&0.84945&0.34703\\
                0.62&0.51181&0.00011&0.00040&0.84535&0.34517\\
                0.66&0.52002&0.00014&0.00051&0.84053&0.34858\\
                0.70&0.52778&0.00017&0.00061&0.83560&0.34818\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_numeric}
    \end{table}

    \begin{table}
        \centering
        \caption{BLEH}
        \begin{ruledtabular}
            \begin{tabular}{c|ccc|ccc}
                & \multicolumn{3}{c|}{Analytic}
                & \multicolumn{3}{c}{Numeric} \\
                \hline
                $N$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                1  \\
                10 \\
                100 \\
                500
            \end{tabular}
        \end{ruledtabular}
        \label{tab:initial_optimum_comparison}
    \end{table}

@@

\appendix
\section{Brute Force Metropolis-Hastings}

    \begin{figure*}
        \makebox[\textwidth][c]{
            \includegraphics[width=1.2\textwidth]{../data/figures/problem_b.pdf}
        }
        \caption{Comparison of analytic and numeric results with the exact
        expression for the energy as a function of $\alpha$. The plots show the
        standard deviation from the blocking method as error ticks. In the
        figure $N$ is the number of particles and $d$ the number of dimensions.}
        \label{fig:initial_problem_b}
    \end{figure*}

\bibliography{references}

\end{document}
